<!-- my-page.html --> 
<script src="https://rawcdn.githack.com/oscarmorrison/md-page/master/md-page.js"></script><noscript>

---
title: "Macaque project data analysis"
output:
  html_document: default
  pdf_document: default
---

```


1. Relationship between seed number and the presence/absence of external events, with trial length as an offset parameter.
  X.seed_nr ~ externalyesno_chr + offset(log(trial_length))
2. Relationship between looking up and the presence/absence of external events, with trial length as an offset parameter.
  up_looking_nr ~ externalyesno_chr + offset(log(trial_length))
3. Relationship between the number of seeds eaten and the number of times the animal looks up, with trial length as an offset parameter.
  X.seed_nr ~ up_looking_per_time + offset(log(trial_length)) # trial for the seed.

```{r, warning = FALSE,message=FALSE, echo=TRUE}
library(brms)
library(ggplot2)

```

#### Get data
```{r}

data <-read.csv("C:/Users/ag-bahl/Desktop/macaque_data/table_day_all.csv")


```



#### Plot of the basic relationship between the total time spent looking up and the number of seeds consumed during the observation period.
```{r , echo=TRUE}
ggplot(data, aes(x = up_tot_time, y= X.seed_nr)) +
  geom_point()+
  ggtitle('The limitation of the number of seeds it eats per time')+
  xlab('Total time pent looking up')+
  ylab('Total seed number per trial')

```

#### 1.Relationship between seed number and the presence/absence of external events, with trial length as an offset parameter.
  X.seed_nr ~ externalyesno_chr + offset(log(trial_length))

```{r, message = FALSE}
model1.1 <-brm(X.seed_nr ~ externalyesno_chr + offset(log(trial_length)), 
               family = poisson, 
               data = data,
               chain = 2)
```

```{r}
summary(model1.1)
```


```{r}
# ?predict.brmsfit
predict(model1.1,newdata = data.frame(externalyesno_chr = c("yes", "no"),
                             trial_length = c(60, 60)))
```


```{r}
mean(data$trial_length)
```


Here we see the relationship with the occurance of an extrenal event and the number of seeds eaten.
```{r}
plot(conditional_effects(model1.1, points = TRUE))
```


Additionally we constrain the model to look at only the 1 minute long trials.
```{r}
plot(conditional_effects(model1.1, points = TRUE,
                         conditions = data.frame(trial_length = c(60, 60))))
```


### I model the relationship between looking up and the occurance of external events.
### 2. up_nr ~ externalyesno_chr + offset(log(trial_length))

```{r, message = FALSE}
model2.1 <-brm(up_nr ~ externalyesno_chr + offset(log(trial_length)), 
               family = poisson, 
               data = data,
               chain = 2)
               
```

```{r}
summary(model2.1)
```


```{r}
# ?predict.brmsfit
predict(model2.1,
        newdata = data.frame(externalyesno_chr = c("yes", "no"),
                             trial_length = c(60, 60)))
```

##### The average trial length:
```{r}
mean(data$trial_length)
```


I model the relationship between looking up and the occurance of external events.

```{r}
plot(conditional_effects(model2.1, points = TRUE))
```


Additionally we constrain the model to look at only the 1 minute long trials.
```{r}
plot(conditional_effects(model2.1, points = TRUE,
                         conditions = data.frame(trial_length = c(60, 60))))
```



3. Relationship between the number of seeds eaten and the number of times the animal looks up, with trial length as an offset parameter.
  X.seed_nr ~ up_nr_min + offset(log(trial_length)) 


```{r}
#data['up_nr_min']<- (data$up_nr/data$trial_length)*60

#data['up_trial'] = (data$up_nr_min)*(data$trial_length/60)
model3.1 <-brm(X.seed_nr ~ up_nr_min + offset(log(trial_length)), 
               family = poisson, 
               data = data,
               chain = 2)
```

```{r}
summary(model3.1)          
```

# Number of times the animal looks up is positively related with the number of seeds the animal eats
```{r}
plot(conditional_effects(model3.1, points = TRUE))
```
